Toxic Code Snippets on Stack Overflow

### 2018-06-19 cloverflow-arxiv/cloverflow.tex
Created a version for arxiv.

\documentclass[10pt,journal,compsoc]{IEEEtran}

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi

\usepackage{booktabs} % For formal tables
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
%\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{amsfonts}
\usepackage{framed}
\usepackage{cleveref}

@@

\lstset{language=Java,
	tabsize=2,
	basicstyle=\ttfamily\footnotesize,
	mathescape=true
}

@@

\newcommand{\squeezeup}{\vspace{-0.5mm}}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\@makecaption}
{\scshape}
{}
{}
{}
\makeatother

@@

\newcommand\FIXME[1]{{\color{red}\textbf{FIXME: #1}}}

% correct bad hyphenation here
%\hyphenation{op-tical net-works semi-conduc-tor}

@@

\author{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}

% The paper headers
\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, Month~2017}%
{Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Toxic Code Snippets on Stack Overflow}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% The publisher's ID mark at the bottom of the page is less important with
% Computer Society journal papers as those publications place the marks
% outside of the main text columns and, therefore, unlike regular IEEE
% journals, the available text space is not reduced by their presence.
% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
% or like this to get the Computer Society new two part style.
%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark (Computer Society jorunal
% papers don't need this extra clearance.)

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples. Due to an absence of a checking
mechanism after the code has been copied to Stack Overflow, they can become
toxic code snippets, i.e.,~they suffer from being outdated or violating the
original software license. We present a study of online code clones on Stack
Overflow and their toxicity by incorporating two developer surveys and a
large-scale code clone detection. A survey of 201 high-reputation Stack Overflow
answerers (33\% response rate) showed that 131 participants (65\%) have ever
been notified of outdated code and 26 of them (20\%) rarely or never fix the
code. 138 answerers (69\%) never check for licensing conflicts between their
copied code snippets and Stack Overflow's CC BY-SA 3.0. A survey of 87 Stack
Overflow visitors shows that they experienced several issues from Stack Overflow
answers: mismatched solutions, outdated solutions, incorrect solutions, and buggy code. 
85\% of them are not aware of CC BY-SA 3.0
license enforced by Stack Overflow, and 66\% never check for license conflicts
when reusing code snippets. Our clone detection found online clone pairs between
72,365 Java code snippets on Stack Overflow and 111 open source projects in the
curated Qualitas corpus. We analysed 2,289 non-trivial online clone candidates.
Our investigation revealed strong evidence that 153 clones have been copied from
a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated
and potentially harmful for reuse. Furthermore, we found 214 code snippets that
could potentially violate the license of their original software and appear 7,112
times in 2,427 GitHub projects.

%Online code clones are code fragments that are copied from software projects or
%online sources to Stack Overflow as examples in questions and answers. % They
%Due to an absence of a checking mechanism after the code has been copied to
%Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
%being outdated or violating the original software license. We present a study
%incorporating several state-of-the-art tools and techniques to automatically
%extract and filter detected online clone pairs between 72,365 Java code snippets
%on Stack Overflow and 111 Java open source projects in the curated Qualitas
%corpus. We discovered and analysed 2,289 non-trivial online clone candidates.
%Our investigation of the online clone pairs revealed strong evidence that 154
%clones have been copied from a Qualitas project to Stack Overflow.  We found 101
%of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
%we found 214 code snippets on Stack Overflow that could potentially violate the license of their
%original software. To better understand the phenomenon, we also surveyed 201 high-reputation Stack Overflow answerers
%(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
%outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
%code. Only 3 answerers explicitly include software licenses in their answers and
%138 answerers (69\%) never check for licensing conflicts between their copied code
%snippets and Stack Overflow's CC BY-SA 3.0.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Code Clone Detection, Stack Overflow, Outdated Code, Software Licensing
\end{IEEEkeywords}}

% make the title area
\maketitle

% To allow for easy dual compilation without having to reenter the
% abstract/keywords data, the \IEEEtitleabstractindextext text will
% not be used in maketitle, but will appear (i.e., to be "transported")
% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
% or transmag modes are not selected <OR> if conference mode is selected 
% - because all conference papers position the abstract like regular
% papers do.
\IEEEdisplaynontitleabstractindextext
% \IEEEdisplaynontitleabstractindextext has no effect when using
% compsoc or transmag under a non-conference mode.

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}

%The popularity of the Internet encourages tremendous amount of source code
% being shared online.
Stack Overflow is a popular online programming community with 7.6 million users,
14 million questions, and 23 million answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}. It allows programmers to ask
questions and give answers to programming problems. The website has found to be
useful for software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for
educational purposes~\cite{Nasehi2012}. On Stack Overflow, each conversation
contains a question and a list of answers. The answers frequently contain at
least one code snippet as a solution to the question asked. We found that the
code snippets are usually not authored directly on the Stack Overflow website
but copied from another location. A snippet in an answer could be copied and
modified from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS) systems.

@@

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones.''
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. % and (3)~code is transferred from one
% software project to another via a Q\&A website;
Similar to classic code clones, i.e.,~clones between software systems, online
code clones can lead to license violations, bug propagation, an introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

@@

Although this activity of online code cloning is well-known, there are only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
on finding the origins of the clones on Q\&A websites.
In this study, we tackle this challenge of establishing the existence of online code 
clones on Stack Overflow, investigate how they occur, and study the potential
effects to software reusing them.
%Using the same analogy, in this study, we are interested in 
Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
``toxic code snippets.''

Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
	Stack Overflow: meta.stackexchange.com/questions/131495, 
	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.,\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

We would like to motivate the readers by giving two examples of toxic code
snippets. The first example is an outdated and potentially license-violating
online code clone in an answer to a Stack Overflow question regarding how to
implement {\small{\texttt{RawComparator}}} in
\textsf{Hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part
of the accepted answer. The snippet shows how \textsf{Hadoop} implements the
{\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}}
class. The code snippet on the right shows another version of the same method,
but at this time extracted from the latest version (as of October 3, 2017) of
\textsf{Hadoop}. We can see that they both are highly similar except a line
containing {\small{\verb|buffer.reset(null,0,0);|}} which was added on November
21, 2014. The added line is intended for cleaning up the reference in the
{\small{\verb|buffer|}} variable and avoid excess heap usage (issue
no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
While this change has already been introduced into the
{\small{\texttt{compare}}} method several years ago, the code example in Stack
Overflow post is still unchanged. %This example shows that inconsistencies
%between online code clones and their originals can lead users of Stack Overflow
%to reuse outdated code.
In addition, the original code snippet of {\small\texttt{WritableComparator}}
class in Hadoop is distributed with Apache license version 2.0 while its cloned
instance on Stack Overflow contains only the {\small{\texttt{compare}}} method
and ignores its license statement on top of the file. There are two potential
issues for this. First, the code snippet may appear to be under Stack Overflow's
CC BY-SA 3.0 instead of its original Apache license. Second, if the code snippet
is copied and incorporated into another software project with a conflicting
license, a legal issue may arise.

@@

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human-readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are entirely different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
%Similar to the first example, the clone code snippet on Stack Overflow does not 
%include its original Apache v.2.0 license.

The two toxic code snippets in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times\footnote{The number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).} 
at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. 
%A quick web search shows
%that the defective {\small{\texttt{humanReadableInt}}} method in the second
%example already appears in approximately 500 projects on GitHub. 
Considering the popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

%The code snippet on Stack Overflow can be outdated. %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them were found to be outdated. %
	% and questionable for being reused.

@@

%\subsection{Experimental Setup}
%\vspace{1ex}
To answer these five research questions, we perform two surveys and an empirical study to
understand the developers' awareness of toxic code snippets on Stack Overflow and to
empirically study the online code clones between Stack Overflow and open source
projects, and their toxicity.

@@

\textbf{The answerer survey:} the survey contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
We selected the participants for the answerer survey based on their Stack Overflow
reputation. On Stack Overflow, a user's reputation reflects how much the
community trusts them. A user earns reputations when he or she receives upvotes
for good questions and useful answers. Accepted answers receive more reputation
score than questions and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site. In this study, we call Stack
Overflow users who have a high reputation ``Stack Overflow answerers.''
The participants were invited to take the survey via email addresses available
on their public Stack Overflow and GitHub profiles. We selected the answerers
based on the all-time reputation ranking\footnote{Stack Overflow Users (data as
	of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
invited participants had a reputation from 963,731 (the highest) to 6,999, and
we sent out 607 emails (excluding undelivered ones, e.g.,\ due to
illegal email addresses). 
The survey was
open for participation for two months, from 25 July to 25 September 2017, before
we collected and analysed the responses.

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. % The archived dump has a size of 9 gigabytes.
The data dump is in XML, and it contains information about posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines is usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking.
Finally, we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippets is 17 lines.

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	%\small
	\begin{tabular}{lrr}
		\toprule
		Data set & No. of files & SLOC \\
		\midrule
		Stack Overflow & 72,365 & 1,840,581 \\ 
		Qualitas &  166,709 & 19,614,083 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. %\textbf{Clone Detection and Configuration: }
There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to the nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data sets. CCFinder reported 8 errors while processing the two data sets. 
Although Simian, SourcererCC, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed. Moreover, Simian and
SourcererCC complement each other as SourcererCC's clone fragments are
always confined to method boundaries while Simian's fragments are not.

@@

		NC & Not clones \\ 
		\bottomrule 
	\end{tabular}  %
	%}
\end{table}

>>>>

\documentclass[10pt,journal]{IEEEtran}

\usepackage{cite}
\usepackage{booktabs} \usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{framed}
\usepackage{cleveref}
\usepackage{newtxtext}
\usepackage{newtxmath}

@@

\lstset{language=Java,
	tabsize=2,
	basicstyle=\ttfamily\footnotesize,
        basewidth=0.56em,
	mathescape=true,
        fontadjust
}

@@

\usepackage{etoolbox}

@@

\overfullrule5pt

@@

\author{
  \IEEEauthorblockN{Chaiyong Ragkhitwetsagul\IEEEauthorrefmark{1},
    Jens Krinke\IEEEauthorrefmark{1}, Matheus
    Paixao\IEEEauthorrefmark{1},
    Giuseppe Bianco\IEEEauthorrefmark{2},
    Rocco Oliveto\IEEEauthorrefmark{2}}\\
  \IEEEauthorblockA{\IEEEauthorrefmark{1}University College London,
    London, UK}\\
  \IEEEauthorblockA{\IEEEauthorrefmark{2}University of Molise,
    Campobasso, Italy}
}

\maketitle

\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples. Due to an absence of a checking
mechanism after the code has been copied to Stack Overflow, they can become
toxic code snippets, i.e.,~they suffer from being outdated or violating the
original software license. We present a study of online code clones on Stack
Overflow and their toxicity by incorporating two developer surveys and a
large-scale code clone detection. A survey of 201 high-reputation Stack Overflow
answerers (33\% response rate) showed that 131 participants (65\%) have ever
been notified of outdated code and 26 of them (20\%) rarely or never fix the
code. 138 answerers (69\%) never check for licensing conflicts between their
copied code snippets and Stack Overflow's CC BY-SA 3.0. A survey of 87 Stack
Overflow visitors shows that they experienced several issues from Stack Overflow
answers: mismatched solutions, outdated solutions, incorrect solutions, and buggy code. 
85\% of them are not aware of CC BY-SA 3.0
license enforced by Stack Overflow, and 66\% never check for license conflicts
when reusing code snippets. Our clone detection found online clone pairs between
72,365 Java code snippets on Stack Overflow and 111 open source projects in the
curated Qualitas corpus. We analysed 2,289 non-trivial online clone candidates.
Our investigation revealed strong evidence that 153 clones have been copied from
a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated
and potentially harmful for reuse. Furthermore, we found 214 code snippets that
could potentially violate the license of their original software and appear 7,112
times in 2,427 GitHub projects.
\end{abstract}

\section{Introduction}\label{sec:introduction}

Stack Overflow is a popular online programming community with 7.6 million users,
14 million questions, and 23 million answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}. It allows programmers to ask
questions and give answers to programming problems. The website has found to be
useful for software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for
educational purposes~\cite{Nasehi2012}. On Stack Overflow, each conversation
contains a question and a list of answers. The answers frequently contain at
least one code snippet as a solution to the question asked. We found that the
code snippets are usually not authored directly on the Stack Overflow website
but copied from another location. A snippet in an answer could be copied and
modified from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS) systems.

@@

We call code snippets that are copied from software systems to online Q\&A
websites (such as Stack Overflow) and vice versa as ``online code clones.''
There are two directions in creating online code clones: (1)~code is cloned from
a software project to a Q\&A website as an example; or (2)~code is cloned from a
Q\&A website to a software project to obtain a functionality, perform a
particular task, or fixing a bug. Similar to classic code clones, i.e.,~clones between software systems, online
code clones can lead to license violations, bug propagation, an introduction of
vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
difficult to locate and fix since the search space in online code corpora is
larger and no longer confined to a local repository.

@@

Although this activity of online code cloning is well-known, there are only a few
empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
on finding the origins of the clones on Q\&A websites.
In this study, we tackle this challenge of establishing the existence of online code 
clones on Stack Overflow, investigate how they occur, and study the potential
effects to software reusing them.
Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
``toxic code snippets.''

Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
  Stack Overflow:\\
  meta.stackexchange.com/questions/131495, .../11705, .../12527,
	.../25956,\\ .../321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.,\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

We would like to motivate the readers by giving two examples of toxic code
snippets. The first example is an outdated and potentially license-violating
online code clone in an answer to a Stack Overflow question regarding how to
implement {\small{\texttt{RawComparator}}} in
\textsf{Hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part
of the accepted answer. The snippet shows how \textsf{Hadoop} implements the
{\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}}
class. The code snippet on the right shows another version of the same method,
but at this time extracted from the latest version (as of October 3, 2017) of
\textsf{Hadoop}. We can see that they both are highly similar except a line
containing {\small{\verb|buffer.reset(null,0,0);|}} which was added on November
21, 2014. The added line is intended for cleaning up the reference in the
{\small{\verb|buffer|}} variable and avoid excess heap usage (issue
no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
While this change has already been introduced into the
{\small{\texttt{compare}}} method several years ago, the code example in Stack
Overflow post is still unchanged. In addition, the original code snippet of {\small\texttt{WritableComparator}}
class in Hadoop is distributed with Apache license version 2.0 while its cloned
instance on Stack Overflow contains only the {\small{\texttt{compare}}} method
and ignores its license statement on top of the file. There are two potential
issues for this. First, the code snippet may appear to be under Stack Overflow's
CC BY-SA 3.0 instead of its original Apache license. Second, if the code snippet
is copied and incorporated into another software project with a conflicting
license, a legal issue may arise.

@@

The second motivating example of outdated online code clones with more
disrupting changes than the first one  can be found in an answer to a Stack
Overflow question regarding how to format files sizes in a human-readable form.
\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
right shows another version of the same method, but at this time extracted from
the latest version of \textsf{Hadoop}. We can see that
they are entirely different. The {\small{\texttt{humanReadableInt}}} method is
rewritten on February 5, 2013 to solve an issue of a race condition
(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).

The two toxic code snippets in our examples have been posted on March 11, 2014 and
April 9, 2009 respectively. They have already been viewed 259 and 2,886 times\footnote{The number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).} 
at
the time of writing this paper (October 3, 2017). Our calculation finds that
there will be a new viewer of the first toxic snippet approximately every 5
days compared to almost every day for the second one. 
Considering the popularity of Stack Overflow, which has more than 50 million developers visiting
each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
spread and grow to hundred or thousand copies within only a year or two.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them were found to be outdated.

@@

To answer these five research questions, we perform two surveys and an empirical study to
understand the developers' awareness of toxic code snippets on Stack Overflow and to
empirically study the online code clones between Stack Overflow and open source
projects, and their toxicity.

@@

\textbf{The answerer survey:} the survey contained
11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
open-ended question for additional comments. The first two questions were
mandatory while the other 9 questions were shown to the participants based on
their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
We selected the participants for the answerer survey based on their Stack Overflow
reputation. On Stack Overflow, a user's reputation reflects how much the
community trusts them. A user earns reputations when he or she receives upvotes
for good questions and useful answers. Accepted answers receive more reputation
score than questions and regular answers\footnote{\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site. In this study, we call Stack
Overflow users who have a high reputation ``Stack Overflow answerers.''
The participants were invited to take the survey via email addresses available
on their public Stack Overflow and GitHub profiles. We selected the answerers
based on the all-time reputation ranking\footnote{Stack Overflow Users (data as
	of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
invited participants had a reputation from 963,731 (the highest) to 6,999, and
we sent out 607 emails (excluding undelivered ones, e.g.,\ due to
illegal email addresses). 
The survey was
open for participation for two months, from 25 July to 25 September 2017, before
we collected and analysed the responses.

@@

\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. The data dump is in XML, and it contains information about posts (questions and
answers). We were interested in code snippets embedded in posts which were
located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
Overflow thread contains a question and several answers. An answer can also be
marked as an \textbf{accepted answer} by the questioner if the solution fixes
his/her problem. We collected Java code snippets using two criteria. First, we
only focused on code snippets in accepted answers. We chose the snippets in
accepted answers because they actually solved the problems in the questions.
Moreover, they are usually displayed just below the questions which makes them
more likely to be reused than other answers. Second, we were only interested in
code snippets of at least ten lines. Although the minimum clone size of six
lines is usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
empirically found that snippets of six lines contain a large number of
boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
methods, which are not interesting for the study. Each snippet was extracted
from the dump and saved to a file. Moreover, we filtered out irrelevant code
snippets that were part of the accepted answers but were not written in Java by
using regular expressions and manual checking.
Finally, we obtained 72,365 Java code snippets containing 1,840,581
lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
source code. The median size of the snippets is 17 lines.

@@

\begin{table}
	\centering
	\caption{Stack Overflow and Qualitas datasets}
	\label{tab:datasets}
	\begin{tabular}{lrr}
		\toprule
		Data set & No. of files & SLOC \\
		\midrule
		Stack Overflow & 72,365 & 1,840,581 \\ 
		Qualitas &  166,709 & 19,614,083 \\ 
		\bottomrule
	\end{tabular} 
\end{table}

\textbf{Clone Detection Tools: } We use clone detection to discover online code
clones. There are a number of restrictions in terms of choosing the clone detection
tools for this study. The main restriction is due to the nature of code snippets
posted on Stack Overflow, as most of them are incomplete Java classes or
methods. Hence, a detector must be flexible enough to process code snippets that
are not compilable or not complete blocks. Moreover, since the amount of code
that has to be processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
while PMD CPD failed to complete the execution due to lexical errors. iClones
could complete its execution but skipped 367 snippets due to malformed blocks in
Stack Overflow data sets. CCFinder reported 8 errors while processing the two data sets. 
Although Simian, SourcererCC, and DECKARD
could successfully report clones, we decided to choose only Simian and
SourcererCC due to their fast detection speed. Moreover, Simian and
SourcererCC complement each other as SourcererCC's clone fragments are
always confined to method boundaries while Simian's fragments are not.

@@

		NC & Not clones \\ 
		\bottomrule 
	\end{tabular}  \end{table}
